Pollution, agricultural productivity, and development: Evidence from coal in plants in India^[All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution_development]

### 2023-01-17 draft/draft.Rmd
small changes to draft

# district
districts <- read_sf(paste0("data/spatial/districts/districts.shp"))
districts <- districts %>% 
                dplyr::select(state = ST_CEN_CD, district = DT_CEN_CD, state_name = ST_NM, district_name = DISTRICT)
districts <- districts %>% filter(state=="02" & district=="02")
# Villages
villages <- read_sf(paste0("data/spatial/villages_overlap/villages_overlap.shp"))
villages <- villages %>% mutate(shrid = paste0(pc11_s_id, "-", pc11_tv_id)) %>%
                          dplyr::select(shrid, state = ST_CEN_CD, district = DT_CEN_CD, state_name = ST_NM, district_name = DISTRICT)
villages <- villages %>% filter(state=="02" & district=="02")
wind <- read_csv(paste0("data/clean/wind_ntl/days/date_2010-1-1.csv")) %>% as_tibble()
wind$days_sum <- apply(wind[,2:8], 1, FUN = "sum")
wind <- wind %>% dplyr::select(shrid, days_sum)
villages <- villages %>% left_join(wind, by = "shrid")
villages <- villages %>% st_set_crs(st_crs(districts))
# and crs for plants
plants1990 <- plants1990 %>% st_transform(st_crs(districts))
plants2010 <- plants2010 %>% st_transform(st_crs(districts))
india_shape2 <- india_shape %>% st_transform(st_crs(districts))

@@

Robustness checks show that this effect is concentrated in the years after the construction of the power plant, which helps decrease concerns around endogeneity since, conditional on the village fixed effect and rainfall, windfall direction across years and seasons is exogenous. Additionally, leads for wind direction do not predict current agricultural productivity, again supporting the identifying assumptions.

While I am not able to explicitly test effects on land productivity, I look at how adults allocate labor over the last seven days using the National Sample Survey and creating a district-level exposure measure based on the timing of the survey for each household. An additional day of wind over the previous week decreases overall labor allocation by 0.027 days. However, all effects on labor allocation are driven by the older half of my sample; these adults see much large decreases in overall labor allocation, self employment, farm employment, and non-farm employment. This is suggestive evidence of productivity effects being driven by the health effects on individuals, though I am not able to rule out direct effects on land productivity with my data.

@@

```{r windexample, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 8, fig.cap = "Wind direction and aggregation examples (2010-01-01)", fig.footer = list("Note: The left figure shows the average wind direction on January 1st, 2010. The points are the location of coal plants on that date. The right figure shows the distribution of pollution exposure in a specific district -- Kangra district in Himachal Pradesh -- on the same date.")}

@@

The biggest issue with using the NSS is that it includes only district-level identifiers. The main exposure variables, on the other hand, are defined at a lower level of aggregation, at the village. I choose to aggregate this village-level exposure to the district level as shown in the second panel of Figure \@ref(fig:windexample). I use the area overlap of the villages with the district to define a weighted average of exposure for the district at a given time. I calculate the area of overlap for each village and the district as well as the overall area of the district and use these variables to define weights for individual villages. Any part of the district that does not overlap with one of the villages -- the white area in Figure \@ref(fig:windexample) -- does not have any exposure and, as such, receives a value of zero for exposure.

@@

To calculate the effects of exposure to pollution on different outcomes, I rely on fixed effects and the differential exposure driven by plausibly exogenous wind direction, conditional on total rainfall. The regession is of the form
\begin{gather} y_{it} = \alpha_{i} + \gamma_{t} + \beta wind_{it} + \delta rain_{it} + \varepsilon_{it}, \end{gather}
where $y_{it}$ is outcome $y$ for unit $i$ at time $t$, $\alpha$ is a geographic fixed effects, $\gamma_t$ is time fixed effects, $wind_{it}$ is exposure to pollution -- defined using wind direction -- and $rain_{it}$ is rainfall. Although I use $i$ and $t$ as subscripts for the fixed effects, note that these change depending on the unit of analysis and the outcome. I explicitly state the level of fixed effects in the tables and results below.

Identification relies on changes in wind direction across time for the same geographic units. In other words, conditional on the fixed effects and rainfall, I assume changes in wind direction are as good as random and uncorrelated with the outcome -- e.g. agricultural productivity -- except through exposure to pollution. One major threat to identification is that the building of a coal plant could lead to a spurious correlation between the exposure variable and the outcome. Specifically, since exposure is defined as zero prior to the building of a coal plant, the exposure variable itself might be endogenous even though wind direction is not. To help allay these concerns, I estimate additional regressions restricting the sample to only time periods after which a given location has a coal plant. I also present results using leads to show that future wind direction does not seem to predict current outcomes.

@@

In addition to serving as an example, Table \@ref(tab:pollutiontable) also helps validate the use of wind direction as a proxy for exposure to pollution. The first two columns include all available years of data while the last two columns restrict estimation only to the years for which the agricultural productivity regressions are estimated. Across all four columns, the story is the same: when the wind is blowing in the direction of a village from a coal plant within 30 kilometers, estimated $\mathrm{PM_{2.5}}$ is substantially higher. The regressions indicate that one additional day of wind in the direction of the village increases mean $\mathrm{PM_{2.5}}$ for the month by between 0.014 and 0.045 $\mathrm{\mu g/m^3}$.

@@

The first column presents the most simple results, with only the wind exposure variable and the fixed effects. The second column adds a rainfall variable -- defined as the total rainfall in the season -- the addition of which is motivated by the fact that changes in wind direction could be correlated with changes in weather. However, the coefficient on the wind exposure variable is completely unchanged by the addition of rainfall, indicating that weather may not be as worrisome of a confounder as thought.

Column three adds district-by-year-by-season fixed effects as an additional robustness checks. This addition decreases the magnitude of the exposure variable but it remains negative and significant. However, part of this may be due to the fact that the new fixed effects soak up much of the variation in the exposure variable, as shown in Figure \@ref(fig:windexample). The last two columns separate the effects into the monsoon season and the winter season, but the overall effect is roughly similar, though rainfall has a larger effect in the monsoon season than the winter season, which is unsurprising.

@@

# Table
colnames(yieldtable) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtable, caption = "Wind direction and agricultural productivity",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(5, bold = TRUE) %>%
  row_spec(9, hline_after = TRUE) %>%
  add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(yieldtablepm) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtablepm, caption = "Particulate matter (PM 2.5) and agricultural productivity",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(5, bold = TRUE) %>%
  row_spec(9, hline_after = TRUE) %>%
  add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

Recall, however, the results from above: coal plants were placed in places with higher average agricultural productivity. This means that the simple regressions in \@ref(tab:yieldtablepm) might actually be biased upwards: although pollution might negatively affect productivity, pollution is higher in more productive areas due to the endogenous placement of coal plants in the study areas. To recover the actual effect of pollution, we need an instrument. If you believe that wind direction is exogenous and, conditional on the fixed effects and rainfall, only affects agricultural productivity through pollution -- which seems reasonable since it is hard to imagine what other variables it might affect -- then it is a valid instrument for pollution.

@@

# Table
colnames(yieldtabletwo) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtabletwo, caption = "Pollution and agricultural productivity, IV estimates",
      align = "cccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3.5cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(c(5,11), bold = TRUE) %>%
  row_spec(c(9:10), hline_after = TRUE) %>%
  add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(yieldtablehet) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtablehet, caption = "Heterogeneity in the effects of pollution on productivity",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(c(13), hline_after = TRUE) %>%
  row_spec(c(11), bold = TRUE) %>%
  add_header_above(c(" ", ">p(50)" = 1, "<=p(50)" = 1, "all" = 3)) %>%
  kable_classic_2()

@@

Column four adds a quadratic in wind to see if the negative effects of pollution on agricultural productivity are increase or decreasing in wind. In column four, the coefficient on the linear term is 0.0004 while the coefficient on the quadratic term is -0.0002, meaning that the effect of wind is decreasing for any days of wind over two. The negative coefficient also indicates that this negative effect is consistently decreasing, meaning the effect gets worse as average wind days gets higher. Note that this is somewhat different from the regressions in the first two columns, which split the sample by the *maximum* days of wind observed in the sample, not the mean.

@@

data <- matrix(NA, nrow = 6, ncol = 3)
rownames(data) <- c("shapefile", "coal plants", "wind", "pollution", "agriculture", "nightlights")
colnames(data) <- c("source", "geographic coverage", "temporal coverage")
data[1,1] <- "Asher et al. (2021)"
data[2,1] <- "Global Energy Monitor"
data[3,1] <- "NCAR"
data[4,1] <- "Hammer et al. (2020)"
data[5,1] <- "Angopadhyay et al. (2022)"
data[6,1] <- "Asher et al. (2021)"
data[1,2] <- "India"
data[2,2] <- "global"
data[3,2] <- "global"
data[4,2] <- "global"
data[5,2] <- "global"
data[6,2] <- "India"
data[1,3] <- " "
data[2,3] <- "yearly"
data[3,3] <- "daily"
data[4,3] <- "monthly"
data[5,3] <- "two seasons/year"
data[6,3] <- "yearly"

# Table
kable(
      data, caption = "Remote sensing data sources",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: NCAR stands for the National Center for Atmospheric Research. Additional information on Global Energy Monitor and NCAR can be found on their websites, at https://globalenergymonitor.org/projects/global-coal-plant-tracker and https://climatedataguide.ucar.edu/, respectively.", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "2cm") %>%
  column_spec(2,width = "4.5cm") %>%
  column_spec(c(3:4),width = "3.5cm") %>%
  kable_styling(latex_options = "HOLD_position") %>%
  kable_classic_2()

@@

# Table
colnames(yieldtablepostplant) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtablepostplant, caption = "Wind direction and agricultural productivity, post-coal plant only",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The sample is restricted to village-years after a coal plant was built near the village. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(5, bold = TRUE) %>%
  row_spec(9, hline_after = TRUE) %>%
  add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_styling(latex_options = "HOLD_position") %>%
  kable_classic_2()

@@

# Table
colnames(yieldtableleads) <- c("(1)", "(2)")
kable(
      yieldtableleads, caption = "Agricultural productivity and pollution leads",
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(c(12), hline_after = TRUE) %>%
  row_spec(c(9), bold = TRUE) %>%
  kable_classic_2()

>>>>

# district
districts <- read_sf(paste0("data/spatial/districts/districts.shp"))
districts <- districts %>% 
                dplyr::select(state = ST_CEN_CD, district = DT_CEN_CD, state_name = ST_NM, district_name = DISTRICT)
districts <- districts %>% filter(state=="23" & district=="07")
# Villages
villages <- read_sf(paste0("data/spatial/villages_overlap/villages_overlap.shp"))
villages <- villages %>% mutate(shrid = paste0(pc11_s_id, "-", pc11_tv_id)) %>%
                          dplyr::select(shrid, state = ST_CEN_CD, district = DT_CEN_CD, state_name = ST_NM, district_name = DISTRICT)
villages <- villages %>% filter(state=="23" & district=="07")
wind <- read_csv(paste0("data/clean/wind_ntl/days/date_2010-1-1.csv")) %>% as_tibble()
wind$days_sum <- apply(wind[,2:8], 1, FUN = "sum")
wind <- wind %>% dplyr::select(shrid, days_sum)
villages <- villages %>% left_join(wind, by = "shrid")
villages <- villages %>% st_set_crs(st_crs(districts))
# and crs for plants
plants1990 <- plants1990 %>% st_transform(st_crs(districts))
plants2010 <- plants2010 %>% st_transform(st_crs(districts))
india_shape2 <- india_shape %>% st_transform(st_crs(districts))

villages <- st_snap(villages, districts, tolerance = 1250)

@@

Robustness checks show that this effect is concentrated in the years after the construction of the power plant, which helps decrease concerns around endogeneity since, conditional on the village fixed effect and weather (rainfall and temperature), wind direction across years and seasons is exogenous. Additionally, leads for wind direction do not predict current agricultural productivity, again supporting the identifying assumptions.

While I am not able to explicitly test effects on land productivity, I look at how adults allocate labor over the last seven days using the National Sample Survey and creating a district-level exposure measure based on the timing of the survey for each household. An additional day of wind over the previous week decreases overall labor allocation by `r paste0(substr(labortable[1,2],2,6))` days. However, all effects on labor allocation are driven by the older half of my sample; these adults see much large decreases in overall labor allocation, self employment, farm employment, and non-farm employment. This is suggestive evidence of productivity effects being driven by the health effects on individuals, though I am not able to rule out direct effects on land productivity with my data.

@@

```{r windexample, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 8, fig.cap = "Wind direction and aggregation examples (2010-01-01)", fig.footer = list("Note: The left figure shows the average wind direction on January 1st, 2010. The points are the location of coal plants on that date. The right figure shows the distribution of pollution exposure in a specific district -- Guna district in Madhya Pradesh -- on the same date.")}

@@

The biggest issue with using the NSS is that it includes only district-level identifiers. The main exposure variables, on the other hand, are defined at a lower level of aggregation, at the village. I choose to aggregate this village-level exposure to the district level as shown in the second panel of Figure \@ref(fig:windexample) -- the district is a randomly selected district in the data, Guna district in Madhya Pradesh. I use the area overlap of the villages with the district to define a weighted average of exposure for the district at a given time. I calculate the area of overlap for each village and the district as well as the overall area of the district and use these variables to define weights for individual villages. Any part of the district that does not overlap with one of the villages -- the white area in Figure \@ref(fig:windexample) -- does not have any exposure and, as such, receives a value of zero for exposure.

@@

To calculate the effects of exposure to pollution on different outcomes, I rely on fixed effects and the differential exposure driven by plausibly exogenous wind direction, conditional on total rainfall and average temperature. The regression is of the form
\begin{gather} y_{it} = \alpha_{i} + \gamma_{t} + \beta wind_{it} + \delta rain_{it} + \psi temp_{it} + \varepsilon_{it}, \end{gather}
where $y_{it}$ is outcome $y$ for unit $i$ at time $t$, $\alpha$ is a geographic fixed effects, $\gamma_t$ is time fixed effects, $wind_{it}$ is exposure to pollution -- defined using wind direction -- $rain_{it}$ is total rainfall during the season, and $temp_{it}$ is average temperature during the season. Although I use $i$ and $t$ as subscripts for the fixed effects, note that these change depending on the unit of analysis and the outcome. I explicitly state the level of fixed effects in the tables and results below.

Identification relies on changes in wind direction across time for the same geographic units. In other words, conditional on the fixed effects and weather, I assume changes in wind direction are as good as random and uncorrelated with the outcome -- e.g. agricultural productivity -- except through exposure to pollution. One major threat to identification is that the building of a coal plant could lead to a spurious correlation between the exposure variable and the outcome. Specifically, since exposure is defined as zero prior to the building of a coal plant, the exposure variable itself might be endogenous even though wind direction is not. To help allay these concerns, I estimate additional regressions restricting the sample to only time periods after which a given location has a coal plant. I also present results using leads to show that future wind direction does not seem to predict current outcomes.

@@

In addition to serving as an example, Table \@ref(tab:pollutiontable) also helps validate the use of wind direction as a proxy for exposure to pollution. The first two columns include all available years of data while the last two columns restrict estimation only to the years for which the agricultural productivity regressions are estimated. Across all four columns, the story is the same: when the wind is blowing in the direction of a village from a coal plant within 30 kilometers, estimated $\mathrm{PM_{2.5}}$ is substantially higher. The regressions indicate that one additional day of wind in the direction of the village increases mean $\mathrm{PM_{2.5}}$ for the month by between `r paste0(substr(pollutiontable[1,2],1,5))` and `r paste0(substr(pollutiontable[1,3],1,5))` $\mathrm{\mu g/m^3}$.

@@

The first column presents the most simple results, with only the wind exposure variable and the fixed effects. The second column adds a rainfall -- defined as the total rainfall in the season -- and average temperature variable, the addition of which is motivated by the fact that changes in wind direction could be correlated with changes in weather. However, the coefficient on the wind exposure variable is completely unchanged by the addition of the two weather variables, indicating that weather may not be as worrisome of a confounder as thought. The direction of the weather coefficients is also consistent with expectations; higher rainfall is good for agricultural productivity while higher temperature is not.

Column three adds district-by-year-by-season fixed effects as an additional robustness checks. This addition decreases the magnitude of the exposure variable but it remains negative and significant. However, part of this may be due to the fact that the new fixed effects soak up much of the variation in the exposure variable, as shown in Figure \@ref(fig:windexample). The last two columns separate the effects into the monsoon season and the winter season, but the overall effect is roughly similar, though rainfall has a larger effect in the monsoon season than the winter season, which is unsurprising given the winter season is driven by irrigation in many areas.

@@

# Table
colnames(yieldtable) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtable, caption = "Wind direction and agricultural productivity",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(7, bold = TRUE) %>%
  row_spec(11, hline_after = TRUE) %>%
  add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(yieldtablepm) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtablepm, caption = "Particulate matter (PM 2.5) and agricultural productivity",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(7, bold = TRUE) %>%
  row_spec(11, hline_after = TRUE) %>%
  add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

Recall, however, the results from above: coal plants were placed in places with higher average agricultural productivity. This means that the simple regressions in \@ref(tab:yieldtablepm) might actually be biased upwards: although pollution might negatively affect productivity, pollution is higher in more productive areas due to the endogenous placement of coal plants in the study areas. To recover the actual effect of pollution, we need an instrument. If you believe that wind direction is exogenous and, conditional on the fixed effects and weather variables, only affects agricultural productivity through pollution -- which seems reasonable since it is hard to imagine what other variables it might affect -- then it is a valid instrument for pollution.

@@

# Table
colnames(yieldtabletwo) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtabletwo, caption = "Pollution and agricultural productivity, IV estimates",
      align = "cccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(c(7,13), bold = TRUE) %>%
  row_spec(c(11:12), hline_after = TRUE) %>%
  add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
yieldtablehet[1,5] <- "0.000"
colnames(yieldtablehet) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtablehet, caption = "Heterogeneity in the effects of pollution on productivity",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(c(15), hline_after = TRUE) %>%
  row_spec(c(13), bold = TRUE) %>%
  add_header_above(c(" ", ">p(50)" = 1, "<=p(50)" = 1, "all" = 3)) %>%
  kable_classic_2()

@@

Column four adds a quadratic in wind to see if the negative effects of pollution on agricultural productivity are increase or decreasing in wind. In column four, the coefficient on the linear term is 0.0006 while the coefficient on the quadratic term is -0.0002, meaning that the effect of wind is decreasing for any days of wind over three The negative coefficient also indicates that this negative effect is consistently decreasing, meaning the effect gets worse as average wind days gets higher. Note that this is somewhat different from the regressions in the first two columns, which split the sample by the *maximum* days of wind observed in the sample, not the mean.

@@

data <- matrix(NA, nrow = 7, ncol = 3)
rownames(data) <- c("shapefile", "coal plants", "wind", "pollution", "agriculture", "nightlights", "weather")
colnames(data) <- c("source", "geographic coverage", "temporal coverage")
data[1,1] <- "Asher et al. (2021)"
data[2,1] <- "Global Energy Monitor"
data[3,1] <- "NCAR"
data[4,1] <- "Hammer et al. (2020)"
data[5,1] <- "Angopadhyay et al. (2022)"
data[6,1] <- "Asher et al. (2021)"
data[7,1] <- "TerraClimate"
data[1,2] <- "India"
data[2,2] <- "global"
data[3,2] <- "global"
data[4,2] <- "global"
data[5,2] <- "global"
data[6,2] <- "India"
data[7,2] <- "global"
data[1,3] <- " "
data[2,3] <- "yearly"
data[3,3] <- "daily"
data[4,3] <- "monthly"
data[5,3] <- "two seasons/year"
data[6,3] <- "yearly"
data[7,3] <- "monthly"

# Table
kable(
      data, caption = "Data sources",
      align = "ccccc", booktabs = TRUE, linesep = "", escape = TRUE
      ) %>%
  footnote(
           general = "Global Energy Monitor: globalenergymonitor.org/projects/global-coal-plant-tracker. NCAR: climatedataguide.ucar.edu/. TerraClimate: www.climatologylab.org/terraclimate.html",
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "2cm") %>%
  column_spec(2,width = "4.5cm") %>%
  column_spec(c(3:4),width = "3.5cm") %>%
  kable_styling(latex_options = "HOLD_position") %>%
  kable_classic_2()

@@

# Table
colnames(yieldtablepostplant) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtablepostplant, caption = "Wind direction and agricultural productivity, post-coal plant only",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The sample is restricted to village-years after a coal plant was built near the village. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(7, bold = TRUE) %>%
  row_spec(11, hline_after = TRUE) %>%
  add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_styling(latex_options = "HOLD_position") %>%
  kable_classic_2()

@@

# Table
colnames(yieldtableleads) <- c("(1)", "(2)")
kable(
      yieldtableleads, caption = "Agricultural productivity and pollution leads",
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(c(14), hline_after = TRUE) %>%
  row_spec(c(11), bold = TRUE) %>%
  kable_classic_2()
